### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@38a9c1bcb3e8abf02dc58524703f3dda58235431 🚀

We also should address the impact of false-negatives on the inference of
process and causity in community ecology. We demonstrated that in model
food webs, false-negatives do not impact the measure of total trophic
levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)), although
we cannot generalize this further to other properties. This has
immediate practical concern for how we design what taxa to sample---does
it matter if the sampled network is fully connected? It has been shown
that the stability of subnetworks can be used to infer the stability of
the metaweb paper beyond a threshold of samples
(\textbf{Song2022RapMon?}). But does this extend to other network
properties? And how can we be sure we are at the threshold at which we
can be confident our sample characterizes the whole system?

To try and sample to avoid all false-negatives is a fool's errand.
Species ranges overlap to form mosaics, which themselves are often
changing in time. Communities and networks don't end in space, and the
interactions that connect species on the `periphery' of a given network
to species outside the spatial extent of a given sample will inevitably
appear as false-negatives in practical samples. The goal should instead
be to sample enough to have a statistically robust estimate of the
current state and empirical change over time of an ecological community
at a given spatial extent and temporal resolution, and to determine what
the sampling effort required the describe the current state prior to
sampling.

>>>>

We also should address the impact of false-negatives on the inference of
process and causality in community ecology. We demonstrated that in
model food webs, false-negatives do not impact the measure of total
trophic levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)),
although we cannot generalize this further to other properties. This has
immediate practical concern for how we design what taxa to sample---does
it matter if the sampled network is fully connected? It has been shown
that the stability of subnetworks can be used to infer the stability of
the metaweb paper beyond a threshold of samples
(\textbf{Song2022RapMon?}). But does this extend to other network
properties? And how can we be sure we are at the threshold at which we
can be confident our sample characterizes the whole system? We suggest
that modeling observation error like we have done here can address these
questions and aid in the design of samples of species interactions. To
try and sample to avoid all false-negatives is a fool's errand. Species
ranges overlap to form mosaics, which themselves are often changing in
time. Communities and networks don't end in space, and the interactions
that connect species on the `periphery' of a given network to species
outside the spatial extent of a given sample will inevitably appear as
false-negatives in practical samples. The goal should instead be to
sample a system enough to have a statistically robust estimate of the
current state and empirical change over time of an ecological community
at a given spatial extent and temporal resolution, and to determine what
the sampling effort required prior to sampling.
